Considering scale in multilayer animal social networks

### 2020-06-23 paper/manuscript.Rmd
work abstract

# Abstract
Scale remains a foundational concept in ecology. Spatial scale, for instance,
has become a central consideration in the way we understand landscape ecology
and animal space use. Meanwhile, social processes can also scale from fine-scale
interactions to co-occurrence to overlapping home ranges and vary within and 
across seasons. Multilayer networks promise the integration of monolayer
animal social networks with the complexity and importance of animal space use
and movement in heterogeneous landscapes. Despite the complex interplay between
social networks and animal space use, there remains an important biological
and methodological gap in our understanding of an animal’s perception of scale.
Here we discuss the role of scale in the context of multilayer networks and
provide a social ungulate case study to illustrate the role of social, spatial,
and temporal scale on multilayer processes. <!--We also present perspectives on
future development and applications of scale in multilayer networks with respect
to: phenotypes and individual fitness, movement ecology and collective movement,
and habitat selection and space use.--> Effective integration of social and spatial
processes, including biologically meaningful scales, within the context of
animal social networks is an emerging area of research. Here, we
incorporate perspectives on how the social environment and spatial processes
are linked across scales in a multilayer context.

>>>>

# Abstract
<!-- Scale remains a foundational concept in ecology. Social processes range from 
fine-scale interactions and co-occurrence to overlapping home ranges. Spatial 
scale has become a central consideration in the way we understand landscape ecology
and animal space use. Temporal variation in sociality and

Multilayer networks promise the explicit integration of social, 
spatial and temporal contexts of animal social networks.

-->

Scale remains a foundational concept in ecology. Spatial scale, for instance,
has become a central consideration in the way we understand landscape ecology
and animal space use. Meanwhile, social processes can range from fine-scale
interactions to co-occurrence and overlapping home ranges. <!-- and vary within and 
across seasons.--> Multilayer networks promise the explicit integration
of the social, spatial and temporal contexts multilayer social networks. 
Given the complex interplay of
sociality and animal space use in heterogeneous landscapes, there remains 
an important gap in our understanding of the influence of scale on animal
social networks. Here we discuss social, spatial and temporal scale in the 
context of multilayer caribou social networks. <!--We also present perspectives on
future development and applications of scale in multilayer networks with respect
to: phenotypes and individual fitness, movement ecology and collective movement,
and habitat selection and space use.--> Effective integration of social and spatial
processes, including biologically meaningful scales, within the context of
animal social networks is an emerging area of research. Here, we
incorporate perspectives on how the social environment and spatial processes
are linked across scales in a multilayer context.
